Neighbourhood

### 2023-01-05 docsrc/documentation/notebooks/household_income.Rmd
get plots for all modules (except loneliness aaaaaaa)

---
title: "Household_Income"
output: html_document
date: "2022-12-16"
bibliography: references.bib  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Household Income

## Data

## Methods

## Results

>>>>

---
title: "Household Income"
output: html_document
bibliography: 
  - "refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiiling the website using the makefile
  #- "../../refs.bib" # useful for debugging.
---

```{r setup, include=FALSE}
source('sphinx_notebook_utils.R')
```

## Household Income

Household disposable income is a well known indicator of mental well-being [@graham2009understanding]. Estimating this is a crucial instrument for the effects of many policy interventions

The output variable is monthly household disposable income. This is calculated as a composite using several variables. Rent, mortgages, and council tax are subtracted from net household income and adjusted by household size. This value is then adjusted for yearly inflation estimates.

$$    hh\_income\_intermediate = ((net\_hh\_income) - (rent + mortgage + council\_tax)) / hh\_size$$
$$    hh\_income = hh\_income\_ * inflation\_factor$$
This produces a continuous distribution of pounds per month available for a household to spend as it likes. This is plotted below with a median income of $~£1250$.

```{r, hh_income_data}
continuous_density("hh_income")  
```

### Methods

  To estimate this variable Ordinary Least Squares (OLS) linear regression is used. This is a common  technique for estimating Gaussian distributed variables that is easy to implement using base R.

### Data

  The formula for this linear regression is given as

  $$hh\_income\_next ~ age + sex + factor(ethnicity) + factor(region) + scale(hh\_income) + factor(job\_sec) + factor(labour\_state) + factor(education\_state) + scale(SF\_12) + factor(housing\_quality)$$
Each variable included is defined as follows. Each variable with discrete values is defined in the data tables section of this documentation [here](https://leeds-mrg.github.io/Minos/documentation/data_tables.html).

- sex. Individual's biological sex. [@dilmaghani2018sexual]
- ethnicity. Individual ethnicity. Discrete string values White British, Black African, etc. [@clemens2014method]
- region. Administrative region of the UK. Discrete strings such as London, North-East. [@brewer2007poverty]
- household income. Previous household income values are a strong indicator of current value. [@dilmaghani2018sexual]
- job_sec. NSSEC code for individual's employment. Ordinal values describing job quality. [@clemens2014method]
- labour state. Is a person employed, unemployed, student etc. Discrete states. [@dilmaghani2018sexual]
- education state. Highest attain qualification. Ordinal values based on UK government education tiers [@eika2019educational]
- SF_12. Mental well-being. Continuous score indicating overall mental-wellbeing. is this an indicator of hh_income? [@viswanathan2005nature]
- housing quality. Ordinal values indicating number of appliances in household. [@brewer2007poverty]

### Results

Model coefficients and diagnostics are displayed below. To summarise
- r squared of 0.21 indicates reasonable fit. 
- Gender not significant. Some ethnicities see increases. Only London has higher income. High quality jobs eanr more. PT employed earn less students earn more. Housing quality strong indicator of higher income. 
- diagnostic plots show underdispersion. Some extreme outlier values need investigating. 
- overall decent fit.

```{r income_output, echo=FALSE}
options(width=120)
ols_output("../../../data/transitions/test/hh_income_2018_2019.rds")
ols_histogram("../../../data/transitions/test/hh_income_2018_2019.rds", "hh_income_next")  
```

### References

### 2023-01-05 docsrc/documentation/notebooks/labour.Rmd
get all current module templates with better formatting in taskbar.
get plots for all modules (except loneliness aaaaaaa)

# Labour

Introductory fluff. Why do we need this module? test reference [@1987:nelson].

@@

## Methods

  What methods are used? Justification due to output data type. explanation of model output.

## Data

  What variables are included? Why is this output chosen. What explanatory variables are used and why are they chosen

## Results

  What are the results. Coefficients tables. diagnostic plots. measures of goodness of fit.

```{r housing_output, echo=FALSE}
options(width=120)
nnet_output("../../../data/transitions/test/labour_nnet_2018_2019.rds") #e.g. ../../../data/transitions/test/housing_clm_2018_2019.rds
```

## References

>>>>

@@

## Labour

Labour state is a measure of what an individual does. There are 8 distinctive categories including employment, unemployment, and retired. 
The encodings of these states can be found [here]](https://leeds-mrg.github.io/Minos/documentation/data_tables.html).

```{r labour_barchart, echo=FALSE}
discrete_barplot("labour_state")
```

### Methods

Labour state is a complex categorical data type. Single layer neural network is a simple way to estimate this state. Use multinom function from R's nnet package. Formula for weights included given as.

$$labour\_state\_next = sex + ethnicity + age + education\_state + SF\_12 + housing\_quality + labour\_state + job\_sec + hh\_income + alcohol\_spending$$

### Data

Variables used in this model. Encodings for discrete variables found in data tables.

- sex. Biological sex male/female.
- ethnicity. Ethnicity e.g. white british. XXXX cite.
- age in years. XXXX cite.
- education. Highest qualification attained. XXXX cite 
- sf12. Mental well-being score. XXXX cite
- housing quality. Number of household appliances. Ordinal 1-3. XXXX cite
- labour_state. Previous labour state. XXXX cite. Probably remove this. dominates prediction..
- nssec. Socioeconomic code of job. Indicates job quality with 1-9 ordinal variable. XXXX cite
- household income. Monthly disposable income of individuals household. XXXX cite.
- alcohol spending. How much is spent on alcohol. XXXX cite. remove.

### Results

  - hard to determine goodness of fit. 
  - use confusion matrix to estimate quality of fit. 
  - employed/retired well predicted. unemployed/student volatile socially and expectedly hard to predict. 
  - some deterministic replacement needed for categories like student that have specific time frames. e.g. three years for a degree.

```{r labour_output, echo=FALSE}
options(width=120)
nnet_output("../../../data/transitions/test/labour_nnet_2018_2019.rds") #e.g. ../../../data/transitions/test/housing_clm_2018_2019.rds
nnet_confusion_matrix("../../../data/transitions/test/labour_nnet_2018_2019.rds", mode='multinom', 'factor(labour_state)')
```

### References

### 2023-01-05 docsrc/documentation/notebooks/neighbourhood.Rmd
get plots for all modules (except loneliness aaaaaaa)

# Neighbourhood

Introductory fluff. Why do we need this module? test reference [@1987:nelson].

```{r setup, include=FALSE}
source('sphinx_notebook_utils.R')
```

## Methods

  What methods are used? Justification due to output data type. explanation of model output.

## Data

@@

```{r housing_output, echo=FALSE}
options(width=120)
clm_output("../../../data/transitions/test/neighbourhood_clm_2014_2017.rds") #e.g. ../../../data/transitions/test/housing_clm_2018_2019.rds
```

## References

>>>>

## Neighbourhood

Neighbourhood quality is an indicator of well-being suggested by the SIPHER-7 XXXX ref and others?.

```{r neighbourhood_setup, include=FALSE}
source('sphinx_notebook_utils.R')
```

### Methods

```{r neighbourhood_barchart, echo=FALSE}
print(table(real_data$neighbourhood_safety))
discrete_barplot("neighbourhood_safety")
getwd()
```

  Neighbourhood data are presented as a likert scale from 1-6 indicating the number of harmful activities that happen in a persons
  neighbourhood for individual health. These include robberies and vandalism with the full encoding available in the data tables.

### Data

@@

```{r housing_output, echo=FALSE}
options(width=120)
clm_barplot("../../../data/transitions/test/neighbourhood_clm_2014_2017.rds", "neighbourhood_safety_next")
clm_output("../../../data/transitions/test/neighbourhood_clm_2014_2017.rds")
```

### References
